\documentclass[margin,line]{resume}
\usepackage{multicol}
\begin{document}
\name{\Large Rebecca Skinner}
\begin{resume}
%__________________________________________________________________________________________________________________
% Contact Information
\section{\mysidestyle \textbf{Contact}}
{\tt rebecca@rebeccaskinner.net} \hfill {\tt www.rebeccaskinner.net}
\hfill {\tt github.com/rebeccaskinner}\\\vspace{0mm}
% 429 Colleen Drive \hfill 816-591-0025 \vspace{0mm}\\\vspace{0mm}%
% OFallon, IL, 62269 \hfill {\tt tim@timskinner.net} \vspace{0mm}\\\vspace{0mm}%
% \hfill {\small \textsl{https://github.com/timskinner}} \textbullet {\small \textsl{https://timskinner.net}} \vspace{0mm}\\\vspace{0mm}

%__________________________________________________________________________________________________________________
% Professional Summary
\section{\mysidestyle \textbf{Summary}}
I have experience as a developer and team lead in a wide variety of programming
environments and architectures, especially in C and C++ Linux systems and
application development. My experience working on a variety of projects and
platforms has as both a team member and a team leader has given me valuable
insights into the software development lifecycle which I am able to leverage in
the development of robust software delivered on time and on budget. My
interpersonal and communication skills, combined with formal education and work
experience in systems architecture and design allow me to work well interfacing
with customers, stakeholders, and other developers in the process of gathering
project requirements, performing cost and timeline estimation, and designing
and implementing solutions to meet customer and business needs.

% \section{\mysidestyle \textbf{Clearance}} DOD Secret Clearance
%__________________________________________________________________________________________________________________
% Skills
\section{\mysidestyle \textbf{Languages}}
C, C++, Haskell, Ruby, Bash, Perl, Javascript, Mathematica, Python, SQL

\section{\mysidestyle \textbf{Libraries}}
POSIX, GNU libc, CUDA, STL, Boost, Gtk+, Netfilter, SQLite, Libvirt, OpenSSL, GSL,
X11, MySQL, libevent, glib, Webroot Rocksafe, Smartfilter, Postgresql, curl,
ImageMagick, libx264, libjpeg, ffmpeg, GnuTLS, avisynth, SDL, FFTW

\section{\mysidestyle \textbf{Tools}}
valgrind, gprof, splint, hlint, ctags, cscope, ack, binutils, Bison, CMake, GNU Make,
GNU Autotools, bitbake

\section{\mysidestyle \textbf{Virtualization}}
Libvirt, Qemu/KVM, LXC, OpenVZ, Xen, VirtualBox, VMWare Workstation, VMWare ESX, VMWare Server

\section{\mysidestyle \textbf{Version Control}}
Git, Subversion, CVS, TeamSource

\section{\mysidestyle \textbf{Networking}}
Netfliter, IPTables, EBTables, Snort, iperf, httpload, tcpdump, wireshark, socat, ntop,
nagios, BIND, OpenVPN, OpenLDAP, kerberos, OpenSSL, GnuTLS, OpenSSH,
metasploit, wget, curl

\section{\mysidestyle \textbf{Documentation}}
\LaTeX, Doxygen, Asciidoc, groff, Visio, Inkscape, Umbrello

\section{\mysidestyle \textbf{Operating Systems}}
Linux x86/x86-64 (Debian, Arch, Fedora, CentOS, Gentoo, Ubuntu, Suse), Linux ARM ({\AA}ngstr\"{o}m), Android, Windows, Mac OS

\section{\mysidestyle \textbf{Other Technical Skills}}
Multithreaded programming, networking, cryptography and PKI, network security,
optimization, AJAX, SOAP, JSON, Object Oriented Programming, Functional
Programming, UML, HTML, CSS, image and video processing

\section{\mysidestyle \textbf{Non-Technical Skills}}
Leadership, communication, team management, project management, public speaking

\newpage
%__________________________________________________________________________________________________________________
%Professional Experience
\section{\mysidestyle \textbf{Employment History}}
\textbf{Camber Corporation}, O'Fallon, IL \hfill \textbf{June 2011 -- Present}\vspace{1mm}\\\vspace{1mm}%
\textit{\small{Cybersecurity}}\vspace{1mm}\\\vspace{0mm}%
\textsl{Sr. Software Developer}\\
At Camber I work as a senior software developer on the CENTS team designing and
developing network training simulators for use by DOD and commercial customers.
My job duties include requirements gathering, software and architectural
design, timeline planning, advising project managers and business owners on the
technical impact of business decisions, working with team leads to create and
delegate tasks, developing software, performing code reviews, performing unit
testing, and working with integration and test engineers on the development of
integration tests.
\vspace{1mm}\\\vspace{0mm}
\begin{itemize}
    \item Developed Traffic Analysis System in Haskell
        \begin{itemize}
            \item Used FFI to create haskell API around existing C libraries
            \item Designed and implemented algorithms to analyze network packet
                data to infer behavioral patterns
            \item Designed and implemented algorithms to infer traffic flows
                for non-stateful protocols
            \item Implemented a system to optimize database transactions to
                manage storage of high volumes of network traffic analysis data
            \item Implemented a web service to provide JSON data containing
                analyzed network information
        \end{itemize}
    \item Developed Network Monitoring System in C
        \begin{itemize}
            \item Designed and implemented a TCP state engine in userspace
            \item Designed and implemented a custom memory allocation system to
                improve performance of packet monitoring performance
            \item Designed and implemented adaptive heuristic-based
                probabilistic datastructures to manage rulesets and perform
                first-stage packet filtration
        \end{itemize}
    \item Developed Linux Kernel Module for Network Testing
        \begin{itemize}
            \item Used C to write a Linux kernel module to perform intelligent
                source and destination NATting for test purposes
            \item Used C to write userspace utilities to generate random sets
                of IP addresses
            \item Used C to write userspace utilities to interact with kernel
                module
        \end{itemize}
    \item Developed Linux Installation Tools
        \begin{itemize}
            \item Used C, Ruby, and Bash to implement tools to automate disk
                  partitioning, disk formatting, hardware detection, network
                  configuration, and package selection and installation for
                  systems running a customized variant of Debian GNU/Linux
              \item Designed and used Ruby to implement tools to automate
                  system configuration based on customer requirements.
        \end{itemize}
    \item Development Process Improvement
        \begin{itemize}
            \item Advocated for and implemented lean development processes,
                resulting in significant increases in developer productivity
                and better timeline estimations
            \item Advocated for and implemented iterative pull-based
                development cycle which allowed the team to begin providing
                monthly software feature updates, greatly increasing the rate
                at which features were delivered to customers
            \item Advocated for and implemented code reviews as a requirement
                for all feature merges
        \end{itemize}
\end{itemize}

\textbf{Techguard Security LLC}, O'Fallon, MO \hfill \textbf{June 2010 -- June 2011}\vspace{1mm}\\\vspace{1mm}%
\textit{\small{Research and Development, Center for Adaptive Technology Security}}\vspace{1mm}\\\vspace{0mm}%
\textsl{Sr. Development Engineer}\\
At Techguard I worked on the design, implementation, and documentation of
algorithms as part of DOD funded research projects and internal research and
development. As a Sr. Software Developer I worked both alone and in team
leadership positions. I have gained experience in developing software to run on
multiple hardware platforms include developing high performance GPU accelerated
programs using CUDA and highly optimized software for embedded applications
running on the ARM architecture.  The documentation and reporting requirements
of my job have allowed me to utilize my excellent communication skills in the
creation of technical status reports and formal papers describing the design
and implementation of software and algorithms. 
\vspace{1mm}\\\vspace{0mm}
\begin{itemize}
    \item Researched, designed, and implemented video compression algorithms
        \begin{itemize}
        % \item Designed and implemented a video compression algorithm capable of
        %       transmitting 2112x480 2D and 3D video at 30fps from an unmanned
        %       ground vehicle over an unreliable 1Mbps connection.
        \item Designed and implemented an algorithm to perform real time
              adaptive video compression based on operator field-of-view using
              region based entropy and framerate scaling.
        % \item Designed and implemented real time video stabilization algorithms in C.
        \item Designed and implemented a system to generate neural-network
              training data in C++.
        % \item Implemented FFT, DCT, generic convolution, colorspace
        %       conversion and chroma subsampling algorithms on x86-64 and CUDA
        %       in Haskell and C.
        % \item Implemented CAVLC, CABLC, Huffman Encoding, Golomb coding, and
        %       run-length encoding on x86-64 and CUDA in C.
        % \item Implemented a multi-frame video compositing system in C.
        % \item Implemented a system to communicate with multiple IP based video
        %       capture devices in C++.
        \item Performed timeline and resource utilization estimates.
        \item Developed and assigned tasks to team members.
        % \item Wrote monthly technical status reports on research and
        %       development progress.
        \item Wrote and published technical whitepapers describing algorithm design and
              performance.
        \item Assisted in modification of hardware to integrate with unmanned
              ground vehicle.
        \end{itemize}
    \item Researched, designed, and implemented decision making and
          cryptographic algorithms as part of a research initiative
        \begin{itemize}
        \item Designed and implemented a distributed N of M key
              validation system in C.
        % \item Designed and implemented a neural-network-like automated decision
        %       making system capable of interfacing with hardware sensors in
        %       Haskell and C.
        \item Designed a system to allow graphical simulation and visualization
              of decision making and key validation system in C using Gtk+.
        \item Wrote technical whitepapers describing the algorithms and
              implementation of the decision making and key verification
              systems.
        \end{itemize}
    \item Created a miniature network data sensor for the ARM platform
        \begin{itemize}
        % \item Created a userspace packet filtering application in C and C using
        %       IPTables and libnetfilter-queue.
        % \item Ported existing C and C++ code written for x86\_64 kernel and
        %       user space to the ARM Linux userspace.
        % \item Designed and implemented a system to read multi-gigabyte files
        %       on a limited memory system in C.
        % \item Developed software to interoperate with multiple network clients
        %       to monitor and control the sensor in C and C++.
        \item Created SOAP services for management of sensor in C.
        \item Created a modified version of the {\AA}ngstr\"{o}m linux distribution for
              use on network sensors.
        \item Used Bitbake to create a build system capable of building an
              image including all custom software for deployment on sensor.
        \item Designed and performed formal throughput testing to evaluate
              performance for the ARM network sensor.
        \item Wrote technical whitepapers detailing sensor performing testing
              methodology and results.
        % \item Took the initiative in suggesting the development of a network
        %       sensor for the ARM platform.
        % \item Researched and selected hardware to be used for the development of
        %       the network sensor.
        % \item Created concept renderings and diagrams as part of a presentation
        %       advocating development of the sensor platform.
        % \item Assisted in the development of marketing and informational
        %       material to assist in procuring funding for further product
        %       development.
        \end{itemize}
    \item Created DNS lookup system for ACL generation
        % \begin{itemize}
        % \item Created an application in C to proxy DNS requests from a web
        %       browser and store results in a MySQL database.
        % \item Created a database using MySQL to store DNS query information.
        % \item Created a web interface for generating DNS requests and
        %       generating ACLS in PHP.
        % \end{itemize}
    \item Ported and optimized existing x86 Linux code to ARM Android.
        % \begin{itemize}
        %     \item Ported x86 Linux code written in C to run on Android using
        %           the Android NDK.
        %     \item Modified existing build system to support Android build
        %           system.
        %     \item Modified Android Java applications to use NDK libraries.
        % \end{itemize}
    % \item Initiated and successfully completed transition from Subversion to
    %       Git.
    %     \begin{itemize}
    %         \item Established procedures and best practices for using git.
    %         \item Trained and mentored team members on git usage.
    %     \end{itemize}
    \item Co-Authored an article for the C4ISR Journal (``Stopping The Noise'' expected publication
          date August 2011).
\end{itemize}

\textbf{EADS North America Defense}, O'Fallon, IL \hfill \textbf{November 2008 -- June 2010}\vspace{1mm}\\\vspace{1mm}%
\textit{\small{Research and Development}}\vspace{1mm}\\\vspace{0mm}%
\textsl{Research Scientist, Team Lead}\\
At EADS I worked as the team lead for the Linux systems development group. As
the systems development team lead I created a completely new design for SLAM-R
2.0 that allowed the product to have greatly enhanced stability and performance
while using modern programming practices to reduce the time to design and
implement new features.  I implemented the core design of the 2.0 version of
SLAM-R and lead a group of developers in implementing requirements within the
new core framework. I was able to perform both team lead and design tasks while
acting as a fully participatory member of the development team. In addition to
design and development as a team lead, I performed fundamental research in
areas related to network security, virtualization, high performance and high
scalability computing, cryptography, and cyber security both independently and on
a team. As a result of the research I produced several presentations and papers
including whitepapers for internal and external publication and a technical
proposal in response to a DARPA BAA.
\vspace{1mm}\\\vspace{0mm}
\begin{itemize}
\item Designed and implemented the core components of the SLAM-R software
%    \begin{itemize}
%        \item Implemented high performance network server processes in C
%        \item Used C and Libvirt to create custom software for creating and
%              managing KVM virtual machines
%        \item Used gnutls to implement TLS encryption of network
%              communications
%        \item Used C to implemented a custom high-scalability IPC mechanism
%        \item Designed and implemented a high performance green threading
%              library with task scheduling in C
%    \end{itemize}
% \item Analyzed software requirements
% \item Created design and implementation plans
\item Developed timelines, release schedules, and component specifications
% \item Developed taskings and time estimates
% \item Assigned and tracked progress of team member tasks
\item Mentored team members
% \item Reviewed code for correctness, efficiency, and standards compliance
% \item Created coding and documentation standards
% \item Interviewed prospective team members
\item Gathered software requirements
% \item Worked independently to create and document Linux based operating system for the SLAM-R appliance.
% \item Worked independently to create GUI and text based installers for the
%       SLAM-R OS and software
\item Worked independently and on teams to perform fundamental research and
      create whitepapers in areas related to simulation, network security,
      virtualization, and high performance computing.
% \item Worked with a team to create designs and draft proposals for DARPA BAAs
\end{itemize}

\textbf{Cymtec Systems}, Creve Coure, Missouri \hfill \textbf{May 2007 -- October 2008}\vspace{1mm}\\\vspace{1mm}%
\textit{\small{Linux Systems Developer}}\vspace{1mm}\\\vspace{0mm}%
At Cymtec I worked individually and on a team as the lead systems developer
working on the Sentry bridging network security appliance and the Scout intrusion
detection system. I lead the design and development of version 2.0 of the
Sentry product, including designing and implementing several key features
including realtime TCP packet reassembly, realtime scanning of network traffic
for malware, URL filtering, LDAP integration with ACLs, a new software update
system, and support of two new hardware platforms. As part of the transition to
new hardware platforms I wrote new device drivers to support Intel hardware
network failover chips as well as modified existing Realtek NIC drivers and the
kernel networking stack for Linux 2.6.18. As the lead developer I was also able
to implement a number of performance optimizations that improved the real time
network scanning and malware detection speed from approximately 100Mbps
sustained to over 800Mbps sustained while decreasing memory utilization from
150MB average to 75MB average when tested on the same hardware platform. I
worked with hardware providers to analyze technical specifications and develop
userspace drivers for a serial LCD interface and worked with third party
software vendors to integrate their licensed IP into the Sentry product.
\vspace{1mm}\\\vspace{0mm}
\begin{itemize}
\item Lead the systems development of both the Sentry and Scout products
% \item Migrated the Sentry and Scout products to two new hardware platforms
\item Designed unified software update system for Sentry and Scout
% \item Created a new event reporting application for Scout
% \item Designed and implemented a new init system for the Linux based Scout OS
% \item Developed a reporting system for deployed Scout units
% \item Updated the Scout web user interface
% \item Migrated existing utilities from Java to C++
% \item Created a unified custom Linux based OS for the Sentry and Scout
%       appliances
\item Created a Linux kernel module to support Intel hardware failover
      chips.
% \item Fixed bugs in the Linux mii network stack
% \item Designed and implemented an embedded LCD configuration application for
%       Sentry
\item Designed and implemented a highly efficient userspace TCP reassembly
      engine in C++.
\item Designed and implemented real-time deep-packet inspection algorithms in C++
% \item Designed and implemented an automated online software update system for
%       appliances
% \item Created a highly efficient XML parsing engine in C++
% \item Created a pluggable alert system for IDS events
% \item Designed and developed LDAP integrated ACLs for Sentry
% \item Analyzed performance of existing Scout and Sentry code and optimized
%       performance
\item Analyzed and reverse engineered network protocols
% \item Created an internal documentation system
% \item Managed source code repositories
\end{itemize}

%\textbf{Kean, Inc}, Jefferson City, Missouri \hfill \textbf{2006}\vspace{1mm}\\\vspace{1mm}%
\textbf{Kean, Inc}, Jefferson City, Missouri \hfill \textbf{August 2006 -- May 2007}\vspace{1mm}\\\vspace{1mm}%
\textit{\small{Software Developer}}\vspace{1mm}\\\vspace{0mm}%
\textsl{Systems Developer}\\
At Keane I worked as a junior developer and tier 3 helpdesk on contract to the
Missouri Department of Revenue on the state drivers license system. I worked
with customers to identify problems, remotely repair systems, and identify and
fix bugs in a large existing codebase. I was also responsible for creating and
pushing out software updates to hundreds of remote locations.
% \vspace{1mm}\\\vspace{0mm}
% \begin{itemize}
% \item Created an automated system for updating zipcodes
% \item Established and documented procedures on repairing corrupted Oracle
%       databases
% \item Performed full software and regression testing
% \item Debugged and fixed memory leaks
% \item Worked with internal and external customers to troubleshoot software
%       failures
% \end{itemize}

\section{\mysidestyle \textbf{Professional Organizations}}
\textbf{ACM}\\ Member in good standing

%__________________________________________________________________________________________________________________
% Education
\section{\mysidestyle \textbf{Education and Training}}
\textbf{BS in Computer Information Systems}\\ DeVry University, Kansas City, Missouri\vspace{1mm}\\\vspace{0mm}%
\textbf{2011 Stanford Online AI Class}\\ Completed the 2011 online Stanford AI course

\end{resume}
\end{document}
