\documentclass[margin,line]{resume}
\usepackage{multicol}
\usepackage{calc}
\usepackage{enumitem}

\newenvironment{skills}{
\begin{list}{\small$\bullet$}{\itemsep=0pt \leftmargin=0em \itemindent=0em \small}
}{
  \end{list}
}

\newenvironment{awards}{
  \begin{list}{\small$\bullet$}{\partopsep=0em \leftmargin=1.0em \itemindent=0em \small}
}{
  \end{list}
}

\newcommand{\smbull}{\small$\bullet$  }

\begin{document}
\name{\Large Syed Nadeem (``Nadeem")}
\address{github.com/nadeemsyed $\bullet$ (213) 985-6803 $\bullet$ snadeem.hameed@gmail.com $\bullet$ linkedin.com/in/nadeem-syed} 
\begin{resume}
%__________________________________________________________________________________________________________________
\section{Summary}

{\small 13+ years of software development experience in building large scale, distributed systems using Python and Go.
}

%__________________________________________________________________________________________________________________
\section{Experience}

{\sl Software Developer IV } \hfill
     Feb 2011 -- Present\\
     \textbf{Rackspace Inc.} \hfill
     San Antonio, TX\\[4pt]
{\small\centering\textit{Go, Python, Docker, Ansible, Git, Jenkins, Opentracing, Prometheus, Grafana, Postgres, SQLite, MongoDB}\par}\vspace*{-\baselineskip}
\vspace{4pt}
{\small Rackspace Private Cloud -- Hummingbird  \hfill  Software Developer IV (Jan 2017 - Present)}\\
{\small\textit{Hummingbird is a drop-in replacement for Openstack
Swift written in Go with significant performance and architectural improvements. https://github.com/troubling/hummingbird}}
\begin{itemize} \itemsep -2pt % reduce space between items
\small\item Worked on rewriting Python based system in Go as well as developing new systems to manage large scale object storage.
\small\item Implemented various features to improve observability using distributed tracing, added metrics support(Prometheus and Grafana)
\small\item Added structured logging to make logs easier to analyze
\small\item Implemented HTTP2 and TLS support for improving end-to-end encryption
\small\item Worked on improving erasure coded object storage engine in Hummingbird
\end{itemize}\vspace*{-\baselineskip} % no space after list
\vspace{4pt}
{\small OpenStack Innovation Center (OSIC) -- Storage  \hfill  Software Developer IV (11m)}\\
{\small\textit{OSIC was a joint investment by Rackspace and Intel to accelerate enterprise adoption of OpenStack.}}
\begin{itemize} \itemsep -2pt % reduce space between items
\small\item Worked on integrating Hummingbird with Openstack Swift, contributed to upstream OpenStack projects. Mentored 4 Swift developers from Intel.
\end{itemize}\vspace*{-\baselineskip} % no space after list
\vspace{4pt}
{\small Rackspace Public Cloud -- Cloud Files  \hfill  Software Developer III (16m)}\\
{\small\textit{A global public cloud object storage system with over 100PB capacity, 75 billion
objects, and serving over 20,000 requests/second.}}
\begin{itemize} \itemsep -2pt % reduce space between items
\small\item Worked on rewriting Cloud Files object layer in golang with huge improvement in performance
\small\item Wrote Heroku plugin in order to sell Cloud Files object storage in Heroku platform
\end{itemize}\vspace{-\baselineskip} % no space after list
\vspace{4pt}
{\small Rackspace CORE web application  \hfill  Software Developer II (3 years)}\\
{\small\textit{CORE is Rackspace internal web application suite used both for Customer Relationship Management (CRM) and Enterprise Resource Planning.}}
\begin{itemize} \itemsep -2pt % reduce space between items
\small\item Implemented CORE OS Upgrade project, which replaced all the PHP code to Python in CORE, also switched CORE to RHEL OS. I got a spot award for delivering the project on-time and without errors. 
\small\item Encore project was designed to convert monolithic CORE application to SOA. Designed and implement first phase of Device Service for Encore project. 
\small\item Removed virtualization app from CORE and moved it to Encore Device Service 
\end{itemize}
\vspace{4pt}

{\sl Senior Software Developer } \hfill
     May 2008 – Aug 2009\\
     \textbf{Persistent Systems Inc.} \hfill
     San Antonio, TX\\[4pt]
{\small\centering\textit{Python, Postgres, Pylons, Ext-JS, SOAP, XMLRPC, Subversion }\par}\vspace*{-\baselineskip}
\vspace{4pt}
\begin{itemize} \itemsep -2pt % reduce space between items
\small\item Worked on planning, management, and execution of the ongoing software maintenance for Rackspace CORE application
\small\item Led the team of 5 offshore developers along with their work prioritization and code reviews.
\end{itemize}
\vspace{-\baselineskip} % no space after list

{\sl Software Developer } \hfill
     July 2005- May 2008\\
     \textbf{Persistent Systems Pvt. Ltd } \hfill
     Nagpur, India\\[4pt]
{\small\centering\textit{Python, C++, SOAP, REST }\par}\vspace*{-\baselineskip}
\vspace{4pt}
\begin{itemize} \itemsep -2pt % reduce space between items
\small\item Designed and implemented an add-in for Microsoft Outlook which synchronizes calendar events, to-do/task items, and address-book contacts between Mirapoint server and Outlook.
\small\item Implemented a Python application that connect selected Nokia phones to a Mirapoint Mail and Calendar server for synchronizing events, tasks and contacts via Intellisync Mobile Suite (IMS). 
\end{itemize}
\vspace{4pt}
%__________________________________________________________________________________________________________________
\section{Education}
% \vspace{4pt}
{\small
  {\sl Master of Science}, Computer Science \hfill
  University of Southern California\\
  Los Angeles \hfill
  Aug 2009 - May 2011
}
\linebreak
\newline
{\small
  {\sl Bachelor of Engineering}, Computer Technology \hfill
  Nagpur Univerity, India\\
  Nagpur, India \hfill
  Aug 2001 - May 2005  
}
\linebreak
\newline
{\small
  {\sl IT-605 Distributed Systems}, Distance Education Program, KReSIT  \hfill
  IIT Bombay, India \\
  Nagpur, India \hfill
  Jan 2004 - May 2004
}
% \vspace{2pt}
%__________________________________________________________________________________________________________________
\section{Volunteer Work}

{\small
  {\sl Teaching Volunteer} \\
  Taught a six month course on ``Computer Science Fundamentals" using Blockly and code.org curriculum
  to a group of middle school refugee students.
}

\end{resume}
\end{document}
